Automating the Ontological Argument

### 2015-12-23 Papers/InProgress/IJCAI/paper.tex
minor updates

We give here a list of examples:
\begin{itemize}
\item Anderson and Getting's 1996, p. 168 \cite[p.168]{AndersonGettings1968}
  use essence without conjunct.
\item  Hazen 1998, p.365 \cite[p.365]{Hazen1998} states: ``G\"odel left this
  clause out in [11], but this appears to have been an oversight--it
  is included in related manuscripts''. There is not mentioning of an
  inconsistency though.
\item Look???, p. 514
\item Oppy 1996, p.226-227 \cite[p.226/227]{Oppy1996}, Oppy 2000, p. 364
  \cite[p.364]{Oppy200}, Oppy 2008, p. 1068 \cite[p.1068]{Oppy2008}:
  Oppy uses: ``A is an essence of x iff for every property B, x has B
  neces- sarily iff A entails B'' (this is from Anderson's
  emendation). Check is this leads to inconsistency as well. In this
  case we may write something like:

 Oppy presents an critical
  assessment in order to conclude that G\"odel's argument fails to
  convince. Oppy apparently does not see that he is assessing an
  inconsistent axiom system (and he in fact creates adaptations that
  suffer the same problems).
\item 
\end{itemize}

@@

\section{Automating HOML in HOL}
\subsection{Outline of the Embedding}
\subsection{Improved Embedding for S5}
We present an improved embedding (syntax and defintion of box) in  Fig.~\ref{QMLS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/QMLS5.png}}
\caption{Improved Embedding of S5} \label{QMLS5}
\end{figure}

>>>>

We give here a list of examples:
\begin{itemize}
\item Anderson and Getting's 1996, p. 168 \cite[p.168]{AndersonGettings1968}
  use essence without conjunct.
\item  Hazen 1998, p.365 \cite[p.365]{Hazen1998} states: ``G\"odel left this
  clause out in [11], but this appears to have been an oversight--it
  is included in related manuscripts''. There is not mentioning of an
  inconsistency though.
\item Look???, p. 514
% \item Oppy 1996, p.226-227 \cite[p.226/227]{Oppy1996}, Oppy 2000, p. 364
%   \cite[p.364]{Oppy200}, Oppy 2008, p. 1068 \cite[p.1068]{Oppy2008}:
%   Oppy uses: ``A is an essence of x iff for every property B, x has B
%   neces- sarily iff A entails B'' (this is from Anderson's
%   emendation). Check is this leads to inconsistency as well. In this
%   case we may write something like:

%  Oppy presents an critical
%   assessment in order to conclude that G\"odel's argument fails to
%   convince. Oppy apparently does not see that he is assessing an
%   inconsistent axiom system (and he in fact creates adaptations that
%   suffer the same problems).
% \item 
\end{itemize}

@@

\section{Automating HOML in HOL}
\subsection{Outline of the Embedding}
Logic textbooks commonly utilise classical higher-order logic (HOL)
\cite{Church} as a meta-language to introduce the syntax and the
semantics of object logics of interest, in which then reasoning
problems in concrete application domains can be modeled and solved
with pen and paper.  In fact, this approach can also be followed to
enable interactive and automated proof for even very challenging
objects logics with existing theorem provers for classical
higher-order logic.

% Just as commonly the case in logic textbooks, in the embeddings
% approach classical higher-order logic is utilised as a meta-language
% to encode the syntax and the semantics of object logics in which the
% proof problems of interest are then modeled in. Modulo the embedding
% state of the art automated theorem provers for classical higher-order
% logic can then be utilised as object logic reasoning tools.

For a computational analysis of G\"odel's ontological argument in this
approach the embedding of modal higher-order logics (MHOL) such as K,
KB and S5 for different domain conditions (possibilist and actualist)
is required. This idea has been successfully followed in related work
\cite{C40}. The embedding of modal higher-order logic is in fact
straightforward. Formulas in MHOL such as are lifted to predicates
over worlds, which are explicitly represented in the approach as
terms. Propositional MHOL such as $\neg \varphi$, $\varphi\vee\psi$
and $\box \varphi$ are then mapped to HOL formulas \ldots.

It is easy
to see that this captures the standard translation \cite{Ohlbach},
which is here (intra-logically) realised in HOL by stating a set of
equations; see also Fig. ~\ref{QMLS5}. New is that also quantifiers 
can be mapped \ldots

The approach is very flexible, KB, S5, domain conditions\ldots

\subsection{Improved Embedding for S5}
We present an improved embedding (syntax and defintion of box) in  Fig.~\ref{QMLS5}).
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/QMLS5.png}}
\caption{Improved Embedding of S5} \label{QMLS5}
\end{figure}
